Appendix 1.E: Preparing country region classifications

### 2023-01-29 PhD_pages/data_appendices/1_E_prepare_region_classifications.qmd
Paper 1: Adding LIS data (and restructuring data prep files)

::: {.callout-note collapse="true" appearance="minimal"}
### Packages and settings
```{python}
from owid import catalog
import pandas as pd

pd.set_option('display.max_rows', None)
```
:::

>>>>

::: {.callout-note collapse="true" appearance="minimal"}
### Packages and settings
```{python}
import pandas as pd
pd.set_option('display.max_rows', None)
```
:::
